### 2024-07-08 basic-statistics.qmd
20240708 - reorder computations

@@

exampleValues <- c(0, 0, 10, 15, 20, 30, 1000)
exampleValues_mean <- mean(exampleValues)
```

@@

#mydata %>% 
#  summarise(across(
#      everything(),
#      .fns = list(
#        n = ~ length(na.omit(.)),
#        missingness = ~ mean(is.na(.)) * 100,
#        M = ~ mean(., na.rm = TRUE),
#        SD = ~ sd(., na.rm = TRUE),
#        min = ~ min(., na.rm = TRUE),
#        max = ~ max(., na.rm = TRUE),
#        range = ~ max(., na.rm = TRUE) - min(., na.rm = TRUE),
#        IQR = ~ IQR(., na.rm = TRUE),
#        mad = ~ mad(., na.rm = TRUE),
#        median = ~ median(., na.rm = TRUE),
#        pseudomedian = ~ DescTools::HodgesLehmann(., na.rm = TRUE),
#        mode = ~ petersenlab::Mode(., multipleModes = "mean"),
#        skewness = ~ psych::skew(., na.rm = TRUE),
#        kurtosis = ~ psych::kurtosi(., na.rm = TRUE)),
#      .names = "{.col}.{.fn}")) %>%
#    pivot_longer(
#      cols = everything(),
#      names_to = c("variable","index"),
#      names_sep = "\\.") %>% 
#    pivot_wider(
#      names_from = index,
#      values_from = value)
```

>>>>

exampleValues <- c(0, 0, 10, 15, 20, 30, 1000)
exampleValues_mean <- apa(mean(exampleValues), 2)
```

@@

@@

#mydata %>% 
#  summarise(across(
#      everything(),
#      .fns = list(
#        n = ~ length(na.omit(.)),
#        missingness = ~ mean(is.na(.)) * 100,
#        M = ~ mean(., na.rm = TRUE),
#        SD = ~ sd(., na.rm = TRUE),
#        min = ~ min(., na.rm = TRUE),
#        max = ~ max(., na.rm = TRUE),
#        range = ~ max(., na.rm = TRUE) - min(., na.rm = TRUE),
#        IQR = ~ IQR(., na.rm = TRUE),
#        MAD = ~ mad(., na.rm = TRUE),
#        median = ~ median(., na.rm = TRUE),
#        pseudomedian = ~ DescTools::HodgesLehmann(., na.rm = TRUE),
#        mode = ~ petersenlab::Mode(., multipleModes = "mean"),
#        skewness = ~ psych::skew(., na.rm = TRUE),
#        kurtosis = ~ psych::kurtosi(., na.rm = TRUE)),
#      .names = "{.col}.{.fn}")) %>%
#    pivot_longer(
#      cols = everything(),
#      names_to = c("variable","index"),
#      names_sep = "\\.") %>% 
#    pivot_wider(
#      names_from = index,
#      values_from = value)
```
